When are Fuzzy Extractors Possible?

### 2015-02-11 trunk/info-bounds/FuzzyExtPossibility-crypto.tex
minor edits to TCC rejection

We define \emph{fuzzy min-entropy} to quantify this property of a noisy source of secrets.  Fuzzy min-entropy measures the success of the adversary when provided with \emph{only} the functionality of the fuzzy extractor, that is, the \emph{ideal} security possible from a noisy distribution.  
High fuzzy min-entropy is necessary for the existence of a fuzzy
extractor. 
% ; moreover, there is evidence that it may be sufficient when only computational security is required.

We ask: \emph{is high fuzzy min-entropy a
  sufficient condition for noise-tolerant key extraction?}
If only computational security is required, recent progress on program
obfuscation gives evidence that fuzzy
min-entropy is indeed sufficient. In contrast,
information-theoretic fuzzy extractors are not known for many
practically relevant sources of high fuzzy min-entropy.

@@

Our construction relies on the fuzzy extractor knowing the precise
distribution of the source $W$.  A more ambitious goal is to design a
single extractor that works for all possible sources.  We show that
this more ambitious goal is impossible: we give a family of sources
with high fuzzy min-entropy for which no single fuzzy extractor is
secure.  This result emphasizes the importance of accurate models
of high entropy sources.

@@

% Fuzzy min-entropy measures the quality of a distribution when provided oracle access to the functionality of a fuzzy extractor.  
Fuzzy min-entropy measures the ideal security of a noisy source of
entropy when used for key derivation, similar to distributional
notions of program obfuscation
(e.g.,~\cite{barak2001possibility,DBLP:conf/stoc/DodisS05,DBLP:conf/tcc/DodisS05};
see \secref{sec:related settings} for discussion).  Superlogarithmic fuzzy min-entropy is \emph{necessary} for nontrivial key extraction~(\propref{prop:fuzz necessary}).

@@

\paragraph{Techniques for Positive Results for a Precisely Known
  Distribution} 
We now explain how to construct a secure sketch for a precisely known
distribution $W$ with fuzzy min-entropy (we already explained how to
construct a fuzzy extractor from it).  We begin with distributions in
which all points in the support have the same probability (so-called
``flat'' distributions).  Consider some subsequent reading $w'$. To
achieve correctness, the sketch algorithm must disambiguate which
point $w\in W$ within distance $t$ of $w'$ was
sketched. Disambiguating multiple points can be accomplished by
universal hashing, as long as the size of hash output space is
slightly greater than the number of possible points. Thus, our sketch
is computed via a universal hash of $w$. To determine the length of
that sketch, consider the heaviest (according to $W$) ball $B^*$ of radius
$t$. Because the distribution is flat, $B^*$ is also the ball with the
most points of nonzero probability. Thus, the length of the sketch
needs to be slightly greater than the logarithm of the number of
non-zero probability point in $B^*$. Since $\Hfuzz(W)$ is
determined by the weight of $B^*$, the number of points cannot be
too high and there will be entropy left after the sketch is published.
%
This remaining entropy is sufficient for extracting a key.

@@

\begin{lemma}
\label{lem:flat hashing} (Proof in \apref{sec:proof of flat hashing})
Let $W$ be a flat with $\Hoo(W)\ge m$.  Then
\consref{cons:universal hash} is a $(\mathcal{M}, \{W\}, m - \log |R|, t)$-known distribution secure sketch with error $\delta \le \frac{\beta_{t}-1}{|R|}$. 
\end{lemma}
%\noindent
%\consref{cons:universal hash} writes down enough information to disambiguate any ball of points.  The remaining entropy for this construction is $\Hav(W |\sketch(W)) = \Hoo(W) - \log \beta_{t} -\log 1/\delta$. For a flat distribution this is within a superlogarithmic factor of optimal~(see Equation~\eqref{eq:fuzz for flat}). By choosing $\delta$ based on $\Hfuzz(W)$ we build $(\sketch, \rec)$ such that $\Hav(W | \sketch(W)) = \omega(\log n)$.

@@

\section{Proof of \lemref{lem:flat hashing}}
\label{sec:proof of flat hashing}
\begin{proof}
We first argue security.  Fix some $W\in\mathcal{W}$. Since $\mathcal{K}$ and $W$ are independent $\Hav(W | \mathcal{K}) = \Hoo(W) = m$.  Then by \cite[Lemma 2.2b]{DBLP:journals/siamcomp/DodisORS08}, $\Hav(W | \mathcal{K}, F(\mathcal{K}, W)) \ge \Hoo(W) - \log |F(\mathcal{W}, W)| \ge m - \log |R|$.

>>>>

\smallskip
We define \emph{fuzzy min-entropy} to quantify this property of a noisy source of secrets.  Fuzzy min-entropy measures the success of the adversary when provided with \emph{only} the functionality of the fuzzy extractor, that is, the \emph{ideal} security possible from a noisy distribution.  
High fuzzy min-entropy is necessary for the existence of a fuzzy
extractor. 
\smallskip

We ask: \emph{is high fuzzy min-entropy a
  sufficient condition for key extraction from noisy sources?}
If only computational security is required, recent progress on program
obfuscation gives evidence that fuzzy
min-entropy is indeed sufficient. In contrast,
information-theoretic fuzzy extractors are not known for many
practically relevant sources of high fuzzy min-entropy. 
\smallskip

@@

\smallskip
Our construction relies on the fuzzy extractor knowing the precise
distribution of the source $W$.  A more ambitious goal is to design a
single extractor that works for all possible sources.  We show that
this more ambitious goal is impossible: we give a family of sources
with high fuzzy min-entropy for which no single fuzzy extractor is
secure.  This result emphasizes the importance of accurate models
of high entropy sources.

@@

% Fuzzy min-entropy measures the quality of a distribution when provided oracle access to the functionality of a fuzzy extractor.  
Fuzzy min-entropy measures the ideal security of a noisy source of
entropy when used for key derivation, similar to distributional
notions of program obfuscation
(e.g.,~\cite{barak2001possibility,DBLP:conf/stoc/DodisS05,DBLP:conf/tcc/DodisS05};
see \secref{sec:related settings} for discussion).  Superlogarithmic fuzzy min-entropy is \emph{necessary} for nontrivial key extraction~(Proposition \ref{prop:fuzz necessary}).

@@

\paragraph{Techniques for Positive Results for a Precisely Known
  Distribution} 
We now explain how to construct a secure sketch for a precisely known
distribution $W$ with fuzzy min-entropy (we already explained how to
construct a fuzzy extractor from it).  We begin with distributions in
which all points in the support have the same probability (so-called
``flat'' distributions).  Consider some subsequent reading $w'$. To
achieve correctness, the sketch algorithm must disambiguate which
point $w\in W$ within distance $t$ of $w'$ was
sketched. Disambiguating multiple points can be accomplished by
universal hashing, as long as the size of hash output space is
slightly greater than the number of possible points. Thus, our sketch
is computed via a universal hash of $w$. To determine the length of
that sketch, consider the heaviest (according to $W$) ball $B^*$ of radius
$t$. Because the distribution is flat, $B^*$ is also the ball with the
most points of nonzero probability. Thus, the length of the sketch
needs to be slightly greater than the logarithm of the number of
non-zero probability points in $B^*$. Since $\Hfuzz(W)$ is
determined by the weight of $B^*$, the number of points cannot be
too high and there will be entropy left after the sketch is published.
%
This remaining entropy suffices to extract a key.

@@

\begin{lemma}
\label{lem:flat hashing}
Let $W$ be a flat with $\Hoo(W)\ge m$.  Then
\consref{cons:universal hash} is a $(\mathcal{M}, \{W\}, m - \log |R|, t)$-known distribution secure sketch with error $\delta \le \frac{\beta_{t}-1}{|R|}$. 
\end{lemma}
\begin{proof}
We first argue security.  Fix some $W\in\mathcal{W}$. Since $\mathcal{K}$ and $W$ are independent $\Hav(W | \mathcal{K}) = \Hoo(W) = m$.  Then by \cite[Lemma 2.2b]{DBLP:journals/siamcomp/DodisORS08}, $\Hav(W | \mathcal{K}, F(\mathcal{K}, W)) \ge \Hoo(W) - \log |F(\mathcal{W}, W)| \ge m - \log |R|$.

%\noindent
%\consref{cons:universal hash} writes down enough information to disambiguate any ball of points.  The remaining entropy for this construction is $\Hav(W |\sketch(W)) = \Hoo(W) - \log \beta_{t} -\log 1/\delta$. For a flat distribution this is within a superlogarithmic factor of optimal~(see Equation~\eqref{eq:fuzz for flat}). By choosing $\delta$ based on $\Hfuzz(W)$ we build $(\sketch, \rec)$ such that $\Hav(W | \sketch(W)) = \omega(\log n)$.

@@

%\section{Proof of \lemref{lem:flat hashing}}
%\label{sec:proof of flat hashing}
